---
title: "my-report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(addOptics)
```

This vignette shows a short example for the addOptics package. 

NB: the addOptics package is just a demonstration package developed during a 
workshop! It does not provide any particularly useful functionality!

The library takes a CSV file with coordinates, calculates Optics clusters, and
returns either DBSCAN or Xi extracted cluster id for each feature. 

The example below use the provided example data (use ?exampledata for 
description, it contains the same data as the external CSV)

```{r}
filepath <- system.file("extdata", "addOpticsExample.csv", package = "addOptics")
opticsXi <- OpticsXtractXi(filepath, 4, 5, 0.0006, 5, 0.0004)
```

```{r}
filepath <- system.file("extdata", "addOpticsExample.csv", package = "addOptics")
opticsDBSCAN <- OpticsXtractDBSCAN(filepath, 4, 5, 0.0006, 5, 0.0004)
```
